Supporting Information

### 2018-03-07 SupportingInformation.Rmd
adding stat_testing plot

source("getcopula.R")
source("OurBiCopSelect.R")
source("FittingCopula_selective_loc.R")
source("aphid_data_calling.R")
source("plankton_north_sea_data_calling.R")
source("NonParamStat.R")
source("copsurrog2d.R")
```

@@

>>>>

source("getcopula.R")
source("OurBiCopSelect.R")
source("FittingCopula_selective_loc.R")
source("aphid_data_calling.R")
source("plankton_north_sea_data_calling.R")
source("NonParamStat.R")
source("copsurrog2d.R")
source("TestStats_multivar_dataset.R")
```

@@

### Stat-testing of Non-parametric analysis (for limited number of datapoints)
```{r stat_testing_plot, echo=F, cache=T, cache.extra=list(seed,mtime("TestStats_multivar_dataset.R"))}
set.seed(seed)

resultsloc<-"./Results/stat_results/stat_testing/"
callfn<-coplist_with_params(spearvals=seq(from=0,to=0.9,by=0.1))
coplist<-callfn$coplist
ncores<-3
res_pt35_rankF<-mclapply(X=coplist,FUN=worker,numpts=35,numsims=100,rank=F,mc.cores=ncores)
res_pt35_rankT<-mclapply(X=coplist,FUN=worker,numpts=35,numsims=100,rank=T,mc.cores=ncores)
res_pt1000_rankF<-mclapply(X=coplist,FUN=worker,numpts=1000,numsims=100,rank=F,mc.cores=ncores)
res_pt1000_rankT<-mclapply(X=coplist,FUN=worker,numpts=1000,numsims=100,rank=T,mc.cores=ncores)
save(res_pt35_rankF,res_pt35_rankT,res_pt1000_rankF,res_pt1000_rankT,file=paste(resultsloc,"StatTestNumericResults.RData",sep=''))

b<-callfn$paramlist
plotter_stat_testing(res_pt35_rankF,"res_pt35_rankF",b)
plotter_stat_testing(res_pt35_rankT,"res_pt35_rankT",b)
plotter_stat_testing(res_pt1000_rankF,"res_pt1000_rankF",b)
plotter_stat_testing(res_pt1000_rankT,"res_pt1000_rankT",b)

<!--Now give the plot a number so it can be refered to-->
```{r stat_testing35,echo=F}
fig_nums("stat_testing35",display=F)
```
![stat_testing_results_datapt_35](./Results/stat_results/stat_testing/res_pt35_rankT.pdf)

```{r stat_testing1000,echo=F}
fig_nums("stat_testing1000",display=F)
```
![stat_testing_results_datapt_1000](./Results/stat_results/stat_testing/res_pt1000_rankT.pdf)
